Temporal Split

### 2023-01-30 workflow/notebooks/temporal-split.Rmd

---
title: "Temporal Split"
date: 2022-01-19
output: 
  github_document:
    html_preview: false
---

@@

```{r temporal-split_perf-95-ci}
perf_dat <- read_csv(here('results','temporal-split','performance_results.csv'))
perf_dat %>% 
  filter(term %in% c('cv_metric_AUC', "AUC")) %>%
  mutate(term = case_when(term == 'cv_metric_AUC' ~ 'train AUROC',
                          term == 'AUC' ~ 'test AUROC',
                          TRUE ~ term)
  ) %>% 
  rename(estimate = .estimate,
         lower = .lower,
         upper = .upper) %>% 
  ggplot(aes(x = estimate, xmin = lower, xmax = upper, y = outcome, color = term)) +
  geom_pointrange(position = position_dodge(width = 0.1)) +
  facet_wrap('dataset') +
  theme_sovacool()
```

>>>>

---
title: "Temporal Split"
date: "`r Sys.Date()`"
output: 
  github_document:
    html_preview: false
---

@@

```{r temporal-split_perf-95-ci}
perf_dat <- read_csv(here('results','temporal-split','performance_results.csv'))
perf_temp_plot <- perf_dat %>% 
  filter(term %in% c('cv_metric_AUC', "AUC")) %>%
  mutate(term = case_when(term == 'cv_metric_AUC' ~ 'train AUROC',
                          term == 'AUC' ~ 'test AUROC',
                          TRUE ~ term)
  ) %>% 
  rename(estimate = .estimate,
         lower = .lower,
         upper = .upper) %>% 
  ggplot(aes(x = estimate, xmin = lower, xmax = upper, y = outcome, color = term)) +
  geom_vline(xintercept = 0.5, linetype = 'dashed') +
  geom_pointrange(position = position_dodge(width = 0.1)) +
  xlim(0,1) +
  facet_wrap('dataset', ncol = 1) +
  coord_flip() +
  theme_sovacool() +
  theme(legend.position = 'top')
perf_temp_plot 
```

### vs 100x train/test splits

```{r perf_100x}
perf_dat_100 <- data.table::fread(here('results', 
                                      'performance_results_aggregated.csv')
                                 ) %>% 
  pivot_longer(c('cv_metric_AUC', "AUC"), 
               names_to = 'term', values_to = 'estimate') %>% 
  mutate(term = case_when(term == 'cv_metric_AUC' ~ 'train AUROC',
                          term == 'AUC' ~ 'test AUROC',
                          TRUE ~ term)
         ) 
perf_100_plot <- perf_dat_100 %>% 
  ggplot(aes(x = estimate, y = outcome, color = term)) +
  geom_vline(xintercept = 0.5, linetype = 'dashed') +
  geom_boxplot() +
  xlim(0,1) +
  facet_wrap('dataset', ncol = 1) +
  coord_flip() +
  theme_sovacool() +
  theme(legend.position = 'top')
perf_100_plot
```
